\chapter{Introduction}

\section{Course Purpose and Learning Objectives}

This introductory chapter explains how the \textbf{Applied Physics in Industrial Design (APID)} project will run, what your team is expected to deliver, and how the hydroponics theme connects design work to applied physics. In this session, you will review the course workflow, assessment structure, teamwork expectations, and support resources before moving into later technical sessions.

By the end of this introduction, you should be able to:
\begin{enumerate}
    \item explain the purpose of the APID project and its project-based learning approach;
    \item describe why hydroponics agriculture is the shared project theme for the semester;
    \item identify the main deliverables, submission routes, and assessment formats used in the module; and
    \item organise your team so that weekly tasks, records, and communication remain manageable throughout the semester.
\end{enumerate}

Table~\ref{tab:session0-key-terms} defines the main terms used throughout this chapter.

\begin{table}[htbp]
\centering
\caption{Key terms introduced in the APID orientation}
\label{tab:session0-key-terms}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{|>{\raggedright\arraybackslash}p{0.2\textwidth}|X|}
\hline
\textbf{Term} & \textbf{Definition} \\
\hline
APID & Applied Physics in Industrial Design, the course that combines product development practice with applied physics reasoning. \\
\hline
Hydroponics agriculture & A method of growing plants without soil by controlling water, nutrients, support structures, and environmental conditions. \\
\hline
LLM & Large Language Model, a generative artificial intelligence tool that can assist with drafting, summarising, or brainstorming but must be checked critically. \\
\hline
CLO & Course Learning Outcome, the formal learning outcome used to structure assessment tasks. \\
\hline
ITEL & Institutional Teaching and E-Learning platform, the university system used for announcements, submission links, and updated deadlines. \\
\hline
PD & Product development, the structured process of turning an opportunity into a product concept, evaluation plan, and communication package. \\
\hline
\end{tabularx}
\end{table}

\section{Project Theme: Hydroponics Agriculture}

This section introduces the semester theme and explains why it is a suitable context for Industrial Physics students. Your team will propose a product related to hydroponics agriculture. The product may operate directly inside a hydroponic system or support hydroponic users, growers, or maintenance workflows.

Hydroponics is a suitable project theme because it requires you to consider several applied physics topics at the same time, including:
\begin{itemize}
    \item fluid transport and pressure losses in nutrient delivery systems;
    \item heat transfer and environmental control for plant growth;
    \item sensing and instrumentation for pH, electrical conductivity, temperature, or flow monitoring; and
    \item materials selection, structural stability, and manufacturability for safe, durable products.
\end{itemize}

The theme therefore keeps the project grounded in industrial design while still demanding technical reasoning. Your task is not merely to propose a visually interesting idea. You are expected to justify why the concept should work, who it serves, and how it can be developed systematically.

\section{Team Formation, Roles, and Working Method}

This section outlines how teams are formed and how work should be organised during the semester. Teams are assigned by the module convenor, usually with four or five students per group. Random grouping is used to create diversity of experience and to simulate professional collaboration with unfamiliar teammates.

Once the group list is published on ITEL, review it immediately. If your name is missing, if you are an exchange student without an assigned team, or if a listed member is no longer attending the module, contact the module convenor as soon as possible.

To keep the project manageable, each team should organise itself around the following practices:
\begin{itemize}
    \item appoint a group leader and rotate the role every one or two weeks so that leadership responsibility is shared;
    \item divide work explicitly, monitor progress, and confirm deadlines during each meeting;
    \item keep written records of decisions, action items, and unresolved issues; and
    \item remain with the same team for the full term unless the module convenor approves a change.
\end{itemize}

Rotating leadership is encouraged because it promotes equitable contribution, distributes management experience, and reduces the risk that planning work is carried by one person only.

\section{Weekly Workflow and Meeting Expectations}

This section explains how the weekly learning cycle operates. Most sessions contain a \textbf{pre-class task}, a \textbf{tutorial discussion}, and a \textbf{post-class revision stage}. Pre-class tasks help your group prepare draft outputs before the tutorial. During class, you will compare ideas, receive feedback, and identify what must be improved. After class, your team should refine the material so that it can be used in later deliverables.

Group meetings may be formal or informal, but they should be purposeful. A useful meeting normally includes:
\begin{enumerate}
    \item a short review of the current task and deadline;
    \item confirmation of who is responsible for each action item;
    \item a check on evidence, references, or calculations still needed; and
    \item a written note of decisions so the same discussion is not repeated later.
\end{enumerate}

During brainstorming stages, short bullet points and sketches are acceptable. In the final report, however, your ideas must be presented as complete, well-supported technical communication.

\section{Deliverables and Assessment Overview}

Table~\ref{tab:session0-deliverables} summarises the major deliverables introduced in this chapter. Exact dates, upload links, and any weighting updates must always be confirmed through ITEL.

\begin{table}[htbp]
\centering
\caption{Major APID deliverables introduced in Session 0}
\label{tab:session0-deliverables}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{|>{\raggedright\arraybackslash}p{0.2\textwidth}|>{\raggedright\arraybackslash}p{0.18\textwidth}|>{\raggedright\arraybackslash}p{0.2\textwidth}|X|}
\hline
\textbf{Deliverable} & \textbf{Typical timing} & \textbf{Submission format} & \textbf{Purpose} \\
\hline
Weekly tutorial exercises & Throughout the semester & PDF or lecturer-specified format via ITEL & Documents your team's progress in needs analysis, specifications, concept generation, and related development tasks. \\
\hline
Practical test components & Selected tutorial sessions & Tutorial files submitted to the relevant weekly ITEL tabs & Demonstrates your individual understanding and contribution through graded tutorial outputs. \\
\hline
Fishbowl assessment & Later in the semester & Live discussion in class & Assesses your ability to explain, defend, and connect design decisions to the group project. \\
\hline
Presentation day & End-of-semester presentation period & Slides, optional demonstration material & Communicates the problem, proposed solution, and reflective learning outcomes to the class. \\
\hline
Multimedia report & After concept development activities & Video file or upload link via ITEL & Shows concept alternatives, concept selection rationale, and planned next steps. \\
\hline
Final report & End of semester & Single group PDF via ITEL & Integrates the full product development process into one self-contained technical report. \\
\hline
\end{tabularx}
\end{table}

\section{Resources, Support, and Project Constraints}

This section highlights the practical constraints that affect the project. The module does not provide a dedicated project budget, so teams should choose scopes and materials realistically. If your concept requires prototype expenses, those costs must be managed by the team unless a different arrangement is approved by the lecturer.

Intellectual property normally remains with the student team unless another formal agreement is made. If your team believes the project has patent potential, discuss ownership, contribution, and disclosure early so that disagreements do not emerge at the end of the semester.

For ongoing support, use these channels first:
\begin{itemize}
    \item ITEL for announcements, links, deadlines, and updated assessment instructions;
    \item tutorial sessions for feedback on technical and design decisions; and
    \item team records, minutes, and shared folders for coordination and evidence tracking.
\end{itemize}

\section{Chapter Summary}

In summary, APID uses a project-based workflow to help you apply physics knowledge within a hydroponics-focused product development project. Your immediate priorities are to understand the deliverables, organise your group, establish a meeting routine, and begin documenting work carefully from the first week. The following sections explain the responsible use of LLMs, the team working rules, and the expectations for each major assessment component.
