\section{Instructions for Practical Test}

For the practical test, you are required to submit \textbf{all} assigned weekly tutorial exercises. While each submission will be reviewed, only the following three tutorial sessions will be formally graded:

\begin{itemize}
    \item Identifying Customer Needs
    \item Product Specification
    \item Concept Generation
\end{itemize}

Submissions must be uploaded via the respective weekly tabs on ITEL.

Although only three tutorials will be graded, the other submissions are still important. They will be used to verify your individual contributions and may be referenced during the presentation session. Therefore, ensure that all tutorial work is completed diligently and submitted on time.

You must use the provided LaTeX template for your submissions. The template can be accessed through the following link: \href{https://itel.ums.edu.my/mod/resource/view.php?id=968033}{Download Me}.

To perform well, it is highly recommended that you follow the frameworks and structures introduced during the tutorial sessions. The assessment will be based on the following attributes:

\subsection{Identifying Customer Needs}
\begin{itemize}
    \item Clarity of Survey Objectives
    \item Quality of Survey Questions and Prompts
    \item Accuracy of Needs Statement Translation
    \item Quantity of Translated Needs per Theme
    \item Number of Translated Themes
    \item Classification of Need Types
    \item Source and Relevance of Customer Statements
\end{itemize}

\subsection{Product Specification}
\begin{itemize}
    \item Importance vs. Needs Table
    \item Functionality-Focused Metrics
    \item Inclusion of Additional Metrics for Key Needs
    \item Justification for Metric Units
    \item Needs-to-Metric Matrix
    \item Competitive Benchmarking Chart (CBC) Metrics
    \item Sources Used for CBC Comparison
    \item Alignment Between CBC and Identified Needs
    \item Bar Plot Comparing Group Concept with Competitors
    \item Proper Table and Figure Captions
\end{itemize}

\subsection{Concept Generation}
\begin{itemize}
    \item Analysis of Primary Functions
    \item Justification for Problem Decomposition Methods
    \item Use of Action Verbs in Function Representation
    \item Quality of Proposed Solutions
    \item Justification for Selected Solutions
    \item Quantity of Proposed Solutions
    \item Variety of Information Sources
    \item Quality of Citations
\end{itemize}
