\section{Multimedia Report}

The multimedia report asks your group to communicate concept development in a concise visual format. Prepare a video of no more than 10 minutes and use English as the primary language of communication.

\subsection{Required Content}

Your video should include the following elements:
\begin{itemize}
    \item the full set of concept sketches produced during concept generation;
    \item the criteria used to evaluate and narrow down those concepts;
    \item a short explanation of how you would test the selected concept if the project continued for several more months; and
    \item a brief discussion of intellectual property considerations, including why patent protection may matter for the concept.
\end{itemize}

\subsection{Production Expectations}

A strong multimedia report is not judged only by editing quality. It should also demonstrate technical understanding and clear reasoning. Aim for:
\begin{itemize}
    \item a logical sequence from concept generation to concept selection;
    \item clear visuals, readable labels, and smooth transitions between topics;
    \item accurate explanations of technical features and design decisions; and
    \item concise narration that stays focused on evidence rather than decoration.
\end{itemize}

\subsection{Submission Guidance}

Unless the lecturer states otherwise, upload the final video or approved access link through ITEL using the required naming convention. Check playback quality before submission and keep a backup copy of the final file.
