
% \section*{Introduction}

\subsection*{Presentation Day}
Each group must prepare one presentation, which can be performed by the best speaker in the group, but is preferably presented by all group members. The presentation should be 10 minutes long, with an additional 5 minutes for questions. It is attended all students taking the module. The main content of the presentation should be a description of the problem addressed by the project, an overview of the application developed, and some reflective remarks on the success of the project.
The presentation is usually given using electronic slides (e.g. Microsoft PowerPoint). Some groups may choose to include a live demonstration of their application, but, with the possibility of unforeseen technical problems, this is risky. We generally recommend that demonstrations are given using pre-prepared slides.
Note that it is the quality of the presentation itself that is assessed, not the quality of the project or the application. To make the day more fun, everyone dresses formally for the group project presentations.
The project presentation schedule will be available two to three weeks before the Presentation Day. You should read carefully the information given and check to see when and where your group will be presenting. The sessions normally start on the hour, and groups are required to arrive during the preceding break to make all necessary preparations (such as copying PowerPoint slides to the main computer and ensure they display properly) before the session starts to ensure a smooth and speedy transition between the presentations during the session.
